Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-12 index.Rmd
minor

selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")

@@

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low, <=), 1 (middle), 2 (High, >=) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

selectInput("quantile_used_all","Enter the quantile to use to define High (>=) and Low (<=) Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

>>>>

selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.1", width = "1000px")

@@

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low, <=), 1 (middle), 2 (High, >=) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.1", width = "1000px")
```

@@

selectInput("quantile_used_all","Enter the quantile to use to define High (>=) and Low (<=) Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.1", width = "1000px")
```
